Structure Learning for $\VAR(p)$ Models

### 2019-04-12 paper.tex
Some cleanup.

  \begin{enumerate}
    \item{$x_j \not\gc x_i$}
    \item{$\forall \tau \in \N_+\ B_{ij}(\tau) = 0$}
    \item{$\mathcal{F}_{j \rightarrow i} \defeq \ln\frac{\xi_i}{\xi_{ij}} = 0$}
    \item{$\H_t^{i} \perp \H_{t - 1}^{j}\ |\ \H_{t - 1}^{-j}$}
    \item{\hl{Wold $A(\tau)$ condition}}
    \item{Tie in the 0s of $S(\omega)^{-1}$, though this isn't immediately directed.}
  \end{enumerate}
\end{theorem}

The equivalence $(1) \iff (3)$ is essentially a restatement of the
definition, but is in line with the seminal work of Geweke
\cite{geweke1982measurement}, \cite{geweke1984}.  Statement (4) means that
$(y - \linE{y}{\H_{t - 1}^{-j}}) \perp (z -
\linE{z}{\H_{t - 1}^{-j}})\ \forall y \in \H_t^i,\ z \in
\H_{t - 1}^j$, which is an appealing geometric statement that
there is no direct feedback from $x_j$ to $x_i$ \cite{lindquist}.

\begin{proof}
$(1) \implies (2)$: The projection for $x_i(t)$ onto $\H_{t - 1}$ is (by definition) given by a form similar to equation \ref{eqn:ar_representation}:

@@

@@

The following propositions justify various modifications of $x(t)$
applied in practice to massage $x(t)$ into a form amenable to more
standard tools.

\begin{theorem}[General Invariance]
  \hl{Under what conditions is this actually true?}

  Let $\zeta(t)$ be a stationary discrete time stochastic process.  Let
  $F, G$ be (possibly nonlinear and time varying) invertible filtering
  operations and $f(t)$, $g(t)$ be perfectly predictable and such that
  $x_j(t) \defeq F(\zeta_j - f)(t), x_i(t) \defeq G(\zeta_i - g)(t)$ are W.S.S.  Then,

\begin{equation}
    x_j \gc x_i \iff \zeta_j \te \zeta_i
  \end{equation}
\end{theorem}

\begin{corollary}[Invariance Under Invertible and Deterministic Modifications]
  Let $F(z), G(z)$ describe univariate and invertible
  linear-time-invariant filters.  And, let $f(t), g(t)$ be perfectly
  predictable processes.  Then,

  \begin{equation}
    x_j \gc x_i \iff F(x_j - f)(t) \gc G(x_i - g)(t)
  \end{equation}
\end{corollary}

@@

\begin{equation}
  \label{eqn:parent_expanion}
  x_i(t) = v_i(t) + \B_{ii}(z)x_i(t) + \sum_{k \in \pa{i}}\B_{ik}(z)x_k(t).
\end{equation}

@@

  \begin{equation}
    \label{eqn:parent_expansion}
    x_i(t) = \wtB_{ii}(z)v_i(t) + \sum_{k \in \pa{i}}\wtB_{ik}(z)x_k(t).
  \end{equation}

@@

  \begin{equation}
    x_i(t) = \A_{ii}(z)v_i(t) + \sum_{k \in \anc{i} \setminus\{i\}}\A_{ik}(z)v_k(t),
  \end{equation}

@@

\begin{proposition}
  \label{prop:ancestor_properties}
  In a Granger-causality graph $\gcg$, if $j \pwgc i$ then at least
  one of the following must hold

@@

@@

\begin{example}
  Firstly, on $n = 4$ nodes, ``diamond'' shapes can lead to cancellation on paths of length 2:

@@

\begin{example}
  A second example on $n = 3$ nodes is also worth examining, in this
  cancellation is a result of differing time lags:

@@

\begin{definition}[Strongly Causal]
  We will say that a Granger-causality graph $\gcg$ is \textit{strongly causal}
if $\gcg$ is a DAG and there is at most 1 directed path between any two nodes.
\end{definition}

@@

\begin{proposition}
  \label{prop:sc_graph_common_anc}
  In a strongly causal graph if $j \in \anc{i}$ and $k \in \anc{i} \cap \anc{j}$ then the unique path from $k$ to $i$ contains $j$.
\end{proposition}
\begin{proof}
  Suppose that there is a path from $k$ to $i$ which does not contain $j$.  In this case, there are multiple paths from $k$ to $i$ (one of which \textit{does} go through $j$ since $j \in \anc{i}$) which contradicts the assumption of strong causality.
\end{proof}

@@

\begin{proposition}
  \label{lem:pwgc_anc}
  If $\gcg$ is a strongly causal DAG then $j \in \anc{i} \implies j \pwgc i$.
\end{proposition}
\begin{proof}
  Since strongly causal graphs are acyclic, this allows us to
  recursively expand the parents of $x_i$ in $\gcg$ in the
  $\VAR(\infty)$ representation of $x(t)$ since we will eventually
  terminate at nodes $d$ such that $\pa{d} = \emptyset$.  To this end,
  examining $x_i$ in equation \ref{eqn:ar_representation}

  \begin{align*}
    x_i(t) &= v_i(t) + \sum_{\tau = 1}^\infty \big[ B_{ii}(\tau)x_i(t - \tau) + \sum_{k \in \pa{i}} B_{ik}(\tau)x_k(t - \tau)\big]\\
    \implies x_i(t) &= (1 - \B_{ii}(z))^{-1} \big[v_i(t) + \sum_{k \in \pa{i}} B_{ik}(\tau)x_k(t - \tau) \big]\\
    &= \sum_{\tau = 1}^\infty \big[C_{ii}(\tau)v_i(t - \tau) + \sum_{k \in \pa{i}} C_{ik}(\tau)x_k(t - \tau)\big].
  \end{align*}

  If $\pa{i} = \emptyset$ then we simply have
  $x_i(t) = \sum_{\tau = 1}^\infty C_{ii}(\tau)v_i(t)$ and
  $C_{ii} = A_{ii}$ from equation \ref{eqn:wold}.

  Applying this relation recursively we can write

  \begin{equation*}
    x_i(t) = \sum_{\tau = 1}^\infty\big[C_{ii}(\tau)v_i(t - \tau) + \sum_{k \in \anc{i}}C_{ik}(\tau)v_k(t - \tau) \big].
  \end{equation*}

@@

That strong conditions need to be placed on the topology of $\gcg$ in
order for lemma \ref{lem:pwgc_anc} to be true can be seen through the
earlier examples.

\begin{lemma}
  If $\gcg$ is strongly causal, then any $\VAR(p)$ system on $\gcg$ is stable if and only if
  $B_{ii}(z)$ is stable for every $i = 1, \ldots, n$.
\end{lemma}
\begin{proof}
\end{proof}

@@

\begin{lemma}
  \label{lem:pwgc_anc}
  If $x_j \pwgc x_i$ then one or more of the following hold

  \begin{enumerate}
    \item{$j \in \anc{i}$}
    \item{$\anc{i}\cap\anc{j} \ne \emptyset$.}
  \end{enumerate}
\end{lemma}

% \begin{remark}
%   This lemma formalizes the intuition of \textit{information flow} in $\gcg$.  We have $x_j \pwgc x_i$ whenever $i$ is descended from $j$, or if they have a common ancestor (call it $k$) and ``information'' from $k$ reaches $j$ before it reaches $i$.
% \end{remark}

\begin{proof}
  Is this true if we take \ref{lem:pwgc_anc} as an axiom?
\end{proof}

@@

  Now, since the graph is strongly causal, path $c$ must overlap with
  path $a$ from $j$ to $i$ otherwise there would be multiple paths
  from $k$ to $i$.  By the same reasoning with paths from $k$ to $j$,
  the path $c$ must also overlap with path $b$ from $k$ to $j$, so in
  fact

@@

@@

    \BlankLine
    \caption{Pairwise Graph Recovery}
    \label{alg:pwgr}
    % \TitleOfAlgo{Pairwise Graph Recovery}
    \Input{Pairwise Granger-causality relations between $n$ processes whose joint Granger-causality relations are known to form a strongly causal DAG $\gcg$.}
    \Output{Edges $E = \{(i, j) \in [n] \times [n]\ |\ i \gc j \}$ of the graph $\gcg = ([n], E)$.}
    \Initialize{$S_0 = [n]$  \texttt{\# unprocessed nodes}\\
      $E_0 = \emptyset$  \texttt{\# edges of }$\gcg$\\
      $P_0 = \emptyset$  \texttt{\# layer by layer driving nodes}\\
      $k = 0$ \texttt{\# a counter used only for notation}}
    \BlankLine
    \While{$S_k \ne \emptyset$}{
      $\widehat{P}_k \leftarrow \{i \in S_{k - 1}\ |\ \forall s \in S_{k - 1}\ s \not\pwgc i\}$  \texttt{\# parents of current layer}\\
      $P_k \leftarrow P_{k - 1} \cup \widehat{P}_k$ \texttt{\# Expand parent set}\\
      $S_k \leftarrow S_{k - 1} \setminus \widehat{P}_k$ \texttt{\# remove from } $S$\\

      \;
      $C_k \leftarrow \{i \in S_k\ |\ \forall s \in S_k\ s \not\pwgc i\}$   \texttt{\# potential children of }$P_k$\\
      $D_k \leftarrow \{(i, j) \in P_k \times C_k\ |\ i \pwgc j \}$  \texttt{\# edges incident on }$C_k$\\
      $E_k \leftarrow E_{k - 1} \cup D_k$ \texttt{\# add edges to }$E$\\

@@

We prove the theorem by establishing the correctness of algorithm (\ref{alg:pwgr}).  The idea is to iteratively ``peel away layers'' of nodes by removing the nodes that have no parents remaining, which always exist since the graph is acyclic.  The additional requirement of strong causality ensures firstly that all actual edges of $\gcg$ manifest in some way as pairwise relations (by proposition \ref{prop:pwgc_anc}), and secondly, as we will see, that parents of $C_k$ are in $P_k$ and can be determined by a pairwise test.
\begin{proof}
% 1. Dispense with trivialities
% 2. Show that hat{P}_k is nonempty
% 3. Show that C_k is nonempty
% 4. Show that edges in D_k are actual edges in G
% 5. show that each edge incident on C_k is in D_k
% 6. Induction

  Firstly, if $n = 0$ or $n = 1$ the algorithm is trivially correct, returning on the first iteration with $E = \emptyset$.  Suppose then that $n > 1$, we will proceed by induction and show that on each step, every edge incident upon a node in $C_k$ is contained in $D_k$, that every edge in $D_k$ is an edge in $\gcg$, and finally that $\bigcup_{k = 1}^n C_k = [n] \setminus \widehat{P}_0$ and that this implies $\big([n], \bigcup_{k = 1}^n D_k\big) = \gcg$.

  On the first iteration of the algorithm ($k = 0$) we have $S_0 = [n]$ and $E_0 = \emptyset$.  The set $\widehat{P}_0$ is non-empty since $\gcg$ is a DAG and therefore there are nodes in $\gcg$ without parents, thence if $\widehat{P}_0 = \emptyset$ proposition \ref{prop:ancestor_properties} would be contradicted.  Now, if $\widehat{P}_0 = [n]$ then the graph necessarily contains no edges and we will correctly return $E = \emptyset$.  On the other hand, if $\widehat{P}_0 \ne [n]$ then $C_0$ must also be non-empty, otherwise there would be driving nodes not included in $\widehat{P}_0$.  Consider now an edge $(i, j) \in D_0$ (again $D_0$ is non-empty for the same reason as $C_0$).  Since $i$ has no parents, we must have $\anc{i}\cap\anc{j} = \emptyset$ and therefore $i \in \anc{j}$, and due to the construction of $C_0$ we in fact have $i \in \pa{j}$, which establishes that every edge in $D_0$ is also an edge in $\gcg$.  Finally consider $j \in C_0$, by proposition \ref{prop:pwgc_anc} and since the parents of $C_0$ must be in $P_0$, we see that every edge incident on $j$ must be present in $D_0$.

@@

Consider now step $K < n$ of algorithm \ref{alg:pwgr}.  By lemma \ref{lem:still_strongly_causal} the graph remains strongly causal after having removed nodes $\bigcup_{k = 0}^K P_k$ from $S$, and we assume for induction that $\bigcup_{k = 1}^K D_k$ are all edges of $\gcg$.

@@

\section{Structure Learning}
\subsection{Local Search Heuristics}

>>>>

  \begin{enumerate}
    \item{$x_j \not\gc x_i$}
    \item{$\forall \tau \in \N_+\ B_{ij}(\tau) = 0$}
    \item{$\mathcal{F}_{j \rightarrow i} \defeq \ln\frac{\xi_i}{\xi_{ij}} = 0$}
    \item{$\H_t^{i} \perp \H_{t - 1}^{j}\ |\ \H_{t - 1}^{-j}$}
    \item{$\linE{x_i(t)}{\H_{t - 1}^{-j}} = \linE{x_i(t)}{\H_{t - 1}}$}
    % \item{\hl{Wold $A(\tau)$ condition}}
    % \item{Tie in the 0s of $S(\omega)^{-1}$, though this isn't immediately directed.}
  \end{enumerate}
\end{theorem}

Statement (4) means that
$(y - \linE{y}{\H_{t - 1}^{-j}}) \perp (z - \linE{z}{\H_{t -
    1}^{-j}})\ \forall y \in \H_t^i,\ z \in \H_{t - 1}^j$, which is an
appealing geometric statement that there is no direct feedback from
$x_j$ to $x_i$ \cite{lindquist}.

\begin{proof}
  The equivalence $(1) \iff (3)$ is essentially a restatement of the
  definition, but is in line with the seminal work of Geweke
  \cite{geweke1982measurement}, \cite{geweke1984}.

  The equivalence $(3) \iff (5)$ is also immediate from the
  definitions i.e. the projections are equal if and only if the errors
  are equal.

  $(1) \implies (2)$: The projection for $x_i(t)$ onto $\H_{t - 1}$ is
  (by definition) given by a form similar to equation
  \ref{eqn:ar_representation}:

@@

\hl{TODO: $(4) \implies (1)$}

@@

% The following propositions justify various modifications of $x(t)$
% applied in practice to massage $x(t)$ into a form amenable to more
% standard tools.

% \begin{theorem}[General Invariance]
%   \hl{Under what conditions is this actually true?}

%   Let $\zeta(t)$ be a stationary discrete time stochastic process.  Let
%   $F, G$ be (possibly nonlinear and time varying) invertible filtering
%   operations and $f(t)$, $g(t)$ be perfectly predictable and such that
%   $x_j(t) \defeq F(\zeta_j - f)(t), x_i(t) \defeq G(\zeta_i - g)(t)$ are W.S.S.  Then,

% \begin{equation}
%     x_j \gc x_i \iff \zeta_j \te \zeta_i
%   \end{equation}
% \end{theorem}

\begin{proposition}[Invariance Under Invertible and Deterministic Modifications]
  Let $x(t)$ be a WSS process with absolutely summable covariance
  sequence, and spectral density uniformly bounded above and below.  Let
  $F(z), G$ represent univariate and invertible
  linear-time-invariant filters.  And, let $f(t), g(t)$ be perfectly
  predictable processes.  Then,

  \begin{equation}
    x_j \gc x_i \iff F(x_j - f)(t) \gc G(x_i - g)(t)
  \end{equation}

\begin{proof}
  \hl{TODO}
\end{proof}
\end{proposition}

@@

\begin{equation}
  \label{eqn:parent_expansion}
  x_i(t) = v_i(t) + \B_{ii}(z)x_i(t) + \sum_{k \in \pa{i}}\B_{ik}(z)x_k(t).
\end{equation}

@@

  \begin{equation}
    x_i(t) = \wtB_{ii}(z)v_i(t) + \sum_{k \in \pa{i}}\wtB_{ik}(z)x_k(t).
  \end{equation}

@@

  \begin{equation}
    \label{eqn:ancestor_expansion}
    x_i(t) = \A_{ii}(z)v_i(t) + \sum_{k \in \anc{i} \setminus\{i\}}\A_{ik}(z)v_k(t),
  \end{equation}

@@

\begin{proposition}
  \label{prop:ancestor_properties}
\hl{Need to refine this to exclude $k \rightarrow i \rightarrow j$ from 2.}

  In a Granger-causality graph $\gcg$, if $j \pwgc i$ then at least
  one of the following must hold

@@

  \hl{TODO: Separate $H_t^i \perp \H_t^j \implies \H_t^i \perp \H_{t - 1}^j\ |\ \H_{t - 1}^i$ into a lemma and consolidate it with lemma 2, 3.}

@@

\begin{example}
  \label{ex:diamond_cancellation}
  Firstly, on $n = 4$ nodes, ``diamond'' shapes can lead to cancellation on paths of length 2:

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
    \caption{Graph Corresponding to Example \ref{ex:diamond_cancellation}}
    \label{fig:diamond_cancellation}
    \includegraphics[width=\linewidth]{hand_drawn_example1.jpg}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \caption{Graph Corresponding to Example \ref{ex:lag_cancellation}}
    \label{fig:lag_cancellation}
    \includegraphics[width=\linewidth]{hand_drawn_example2.jpg}
  \end{subfigure}
\end{figure}

\begin{example}
  \label{ex:lag_cancellation}
  A second example on $n = 3$ nodes is also worth examining, in this case
  cancellation is a result of differing time lags:

@@

\begin{definition}[Strongly Causal]
  We will say that a Granger-causality graph $\gcg$ is \textit{strongly causal}
if there is at most 1 directed path between any two nodes.

\hl{TODO: Should DAG be included in this definition?  I think it is
  not necessary for some theorems.}
\end{definition}

@@

\begin{lemma}
  \label{prop:sc_graph_common_anc}
  In a strongly causal graph if $j \in \anc{i}$ and $k \in \anc{i} \cap \anc{j}$ then the unique path from $k$ to $i$ contains $j$.
\end{lemma}
\begin{proof}
  Suppose that there is a path from $k$ to $i$ which does not contain $j$.  In this case, there are multiple paths from $k$ to $i$ (one of which \textit{does} go through $j$ since $j \in \anc{i}$) which contradicts the assumption of strong causality.
\end{proof}

@@

\begin{proposition}
  \label{lem:pwgc_anc}
  If $\gcg$ is a strongly causal DAG then $j \in \anc{i} \implies j \pwgc i$.
\end{proposition}
\begin{proof}
  Using the representation of equation (\ref{eqn:parent_expansion}) we can represent $x_i(t)$ as

  \begin{equation*}
    x_i(t) = v_i(t) + \B_{ii}(z) x_i(t) + \sum_{k \in \pa{i}}\B_{ik}(z) x_k(t).
  \end{equation*}

  In order to show that $j \pwgc i$ we can show (due to theorem (\ref{thm:granger_causality_equivalences})) that

  \begin{equation*}
    \linE{x_i(t)}{\H_{t - 1}^{(i)}} = \linE{x_i(t)}{\H_{t - 1}^{(i, j)}},
  \end{equation*}

\hl{WIP}

% this allows us to recursively expand the
%   parents of $x_i$ in $\gcg$ in the $\VAR(\infty)$ representation of
%   $x(t)$ since we will eventually terminate at nodes $d$ such that
%   $\pa{d} = \emptyset$.  To this end, examining $x_i$ in equation
%   \ref{eqn:ar_representation}

%   \begin{align*}
%     x_i(t) &= v_i(t) + \sum_{\tau = 1}^\infty \big[ B_{ii}(\tau)x_i(t - \tau) + \sum_{k \in \pa{i}} B_{ik}(\tau)x_k(t - \tau)\big]\\
%     \implies x_i(t) &= (1 - \B_{ii}(z))^{-1} \big[v_i(t) + \sum_{k \in \pa{i}} B_{ik}(\tau)x_k(t - \tau) \big]\\
%     &= \sum_{\tau = 1}^\infty \big[C_{ii}(\tau)v_i(t - \tau) + \sum_{k \in \pa{i}} C_{ik}(\tau)x_k(t - \tau)\big].
%   \end{align*}

%   If $\pa{i} = \emptyset$ then we simply have
%   $x_i(t) = \sum_{\tau = 1}^\infty C_{ii}(\tau)v_i(t)$ and
%   $C_{ii} = A_{ii}$ from equation \ref{eqn:wold}.

%   Applying this relation recursively we can write

%   \begin{equation*}
%     x_i(t) = \sum_{\tau = 1}^\infty\big[C_{ii}(\tau)v_i(t - \tau) + \sum_{k \in \anc{i}}C_{ik}(\tau)v_k(t - \tau) \big].
%   \end{equation*}

@@

That strong conditions need to be placed on the topology of $\gcg$ in
order for proposition \ref{lem:pwgc_anc} to be true can be seen through the
earlier examples.

\begin{lemma}
  If $\gcg$ is strongly causal, then any $\VAR(p)$ system on $\gcg$ is stable if and only if
  $B_{ii}(z)$ is stable for every $i = 1, \ldots, n$.
\end{lemma}
\begin{proof}
  \hl{This is certainly true, but I don't think I need to use it anywhere.}
\end{proof}

@@

@@

  Now, since the graph is strongly causal, path $c$ must overlap with
  path $a$ from $j$ to $i$ otherwise there would be multiple paths
  from $k$ to $i$.  By the same reasoning with paths from $k$ to $j$,
  the path $c$ must also overlap with path $b$ from $k$ to $j$, so in
  fact path $c$ from $k$ to $i$ is
  $c = b \rightarrow j \rightarrow a$.

  \hl{TODO: We need the strengthening of prop }(\ref{prop:ancestor_properties})\hl{in order to conclude.}

@@

\subsection{Recovering $\gcg$ via Pairwise Tests}
In this section we will show that if $\gcg$ is a strongly causal DAG, then it is possible to recover $\gcg$ via pairwise tests alone.  This is an interesting fact in and of itself, but also has some implications for applications since pairwise testing is trivially parallelizable.  In section \ref{sec:structure_learning} we will also analyze the use of pairwise testing as a heuristic for general graphs.

@@

    \BlankLine
    \caption{Pairwise Graph Recovery}
    \label{alg:pwgr}
    % \TitleOfAlgo{Pairwise Graph Recovery}
    \Input{Pairwise Granger-causality relations between $n$ processes whose joint Granger-causality relations are known to form a strongly causal DAG $\gcg$.}
    \Output{Edges $E = \{(i, j) \in [n] \times [n]\ |\ i \gc j \}$ of the graph $\gcg = ([n], E)$.}
    \Initialize{$S_0 = [n]$  \texttt{\# unprocessed nodes}\\
      $E = \emptyset$  \texttt{\# edges of }$\gcg$\\
      % $P_0 = \emptyset$  \texttt{\# layer by layer driving nodes}\\
      $k = 0$ \texttt{\# a counter used only for notation}}
    \BlankLine
    \While{$S_k \ne \emptyset$}{
      $\widehat{P}_k \leftarrow \{i \in S_{k - 1}\ |\ \forall s \in S_{k - 1}\ s \not\pwgc i\}$  \texttt{\# parents of current layer}\\
      % $P_k \leftarrow P_{k - 1} \cup \widehat{P}_k$ \texttt{\# Expand parent set}\\
      $S_{k + 1} \leftarrow S_k \setminus \widehat{P}_k$ \texttt{\# remove from } $S$\\

      \;
      $C_k \leftarrow \{i \in S_{k + 1}\ |\ \forall s \in S_{k + 1}\ s \not\pwgc i\}$   \texttt{\# potential children of }$P_k$\\

      \For{$r = 0, \ldots, k$}
      {
        $D_{kr} \leftarrow \{(i, j) \in \widehat{P}_{k - r} \times C_k\ |\ i \pwgc j,\ \text{no } i \rightarrow j \text{ path in } E \}$\\%  \texttt{\# edges incident on }$C_k$\\
        $E \leftarrow E \cup D_{kr}$ \texttt{\# add edges to }$E$\\
      }

@@

We prove the theorem by establishing the correctness of algorithm (\ref{alg:pwgr}).  The idea is to iteratively ``peel away layers'' of nodes by removing the nodes that have no parents remaining, which always exist since the graph is acyclic.  The additional requirement of strong causality ensures firstly that all actual edges of $\gcg$ manifest in some way as pairwise relations (by proposition \ref{prop:pwgc_anc}), and secondly, as we will see, that parents of $C_k$ are in $\bigcup_{r = 0}^k\widehat{P}_{k - r}$ and can be determined by a pairwise test.

\begin{example}
  That we need to proceed backwards through $\widehat{P}_{k - r}$ can be seen from the example of figure \ref{fig:example_fig3}, where if $D_k = \{(i, j) \in \Big(\bigcup_{r = 0}^k \widehat{P}_{k - r}\Big) \times C_k\ |\ i \pwgc j \}$ above we would infer the false positive edge $2 \rightarrow 3$.  Moreover, the same example shows that if simply $D_k = \{(i, j) \in \widehat{P}_k \times C_k\ |\ i \pwgc j \}$, then the edge $1 \rightarrow 3$ would be missed.

\hl{TODO: Inkscape figure}

  \begin{figure}
    \centering
    \label{fig:example_fig3}
    \caption{Example graph for Algorithm \ref{alg:pwgr}}
    \includegraphics[width=0.5\linewidth]{hand_drawn_example3.jpg}
  \end{figure}
\end{example}

\begin{proof}
% 1. Dispense with trivialities
% 2. Show that hat{P}_k is nonempty
% 3. Show that C_k is nonempty
% 4. Show that edges in D_k are actual edges in G
% 5. show that each edge incident on C_k is in D_k
% 6. Induction

  Firstly, if $n = 0$ or $n = 1$ the algorithm is trivially correct, returning on the first iteration with $E = \emptyset$.  Suppose then that $n > 1$, we will proceed by induction.

On the first iteration of the algorithm ($k = 0$) we have $S_0 = [n]$ and $E = \emptyset$.  The set $\widehat{P}_0$ is non-empty since $\gcg$ is a DAG and therefore there are nodes in $\gcg$ without parents, thence if $\widehat{P}_0 = \emptyset$ proposition \ref{prop:ancestor_properties} would be contradicted.  Now, if $\widehat{P}_0 = [n]$ then the graph necessarily contains no edges and we will correctly return $E = \emptyset$.  On the other hand, if $\widehat{P}_0 \ne [n]$ then $C_0$ must also be non-empty, otherwise there would be driving nodes not included in $\widehat{P}_0$.  Consider now an edge $(i, j) \in D_0$ ($D_0$ is non-empty for the same reason as $C_0$).  Since $i$ has no parents, $\anc{i} \cap \anc{j} = \emptyset$ and therefore $i \in \anc{j}$ (proposition \ref{prop:ancestor_properties}).  Furthermore, the construction of $C_k$ implies that $i \in \pa{j}$ since otherwise, there would be some $u \in \anc{j}$ with $i \in \anc{u}$, but then by proposition \ref{lem:pwgc_anc} $i \pwgc u$ and $u \pwgc j$ so that $u \not \in \widehat{P}_0 \implies u \in S_0 \implies j \not\in C_0$, a contradiction.

% and show that on each step, every edge incident upon a node in $C_k$ is contained in $D_k$, that every edge in $D_k$ is an edge in $\gcg$, and finally that $\bigcup_{k = 1}^n C_k = [n] \setminus \widehat{P}_0$ and that this implies $\big([n], \bigcup_{k = 1}^n D_k\big) = \gcg$.

%  On the first iteration of the algorithm ($k = 0$) we have $S_0 = [n]$ and $E_0 = \emptyset$.  The set $\widehat{P}_0$ is non-empty since $\gcg$ is a DAG and therefore there are nodes in $\gcg$ without parents, thence if $\widehat{P}_0 = \emptyset$ proposition \ref{prop:ancestor_properties} would be contradicted.  Now, if $\widehat{P}_0 = [n]$ then the graph necessarily contains no edges and we will correctly return $E = \emptyset$.  On the other hand, if $\widehat{P}_0 \ne [n]$ then $C_0$ must also be non-empty, otherwise there would be driving nodes not included in $\widehat{P}_0$.  Consider now an edge $(i, j) \in D_0$ (again $D_0$ is non-empty for the same reason as $C_0$).  Since $i$ has no parents, we must have $\anc{i}\cap\anc{j} = \emptyset$ and therefore $i \in \anc{j}$, and due to the construction of $C_0$ we in fact have $i \in \pa{j}$, which establishes that every edge in $D_0$ is also an edge in $\gcg$.  Finally consider $j \in C_0$, by proposition \ref{prop:pwgc_anc} and since the parents of $C_0$ must be in $P_0$, we see that every edge incident on $j$ must be present in $D_0$.

@@

%Consider now step $K < n$ of algorithm \ref{alg:pwgr}.  By lemma \ref{lem:still_strongly_causal} the graph remains strongly causal after having removed nodes $\bigcup_{k = 0}^K P_k$ from $S$, and we assume for induction that $\bigcup_{k = 1}^K D_k$ are all edges of $\gcg$.

@@

\section{Structure Learning}
\label{sec:structure_learning}
\subsection{Local Search Heuristics}
